---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggpivot

<!-- badges: start -->
<!-- badges: end -->

The goal of ggpivot is to make tables w ggplot2.

Specify x and y categorical variables; let ggplot2 count number of observations or calculate proportions.

## Installation


And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("EvaMaeRey/ggpivot")
```

```{r}
library(tidyverse)
library(magrittr)
```

# a geom that counts categories and prints the count

```{r}
geom_text_twowaycount_script <- readLines("./R/geom_text_twowaycount.R")
```

```{r count, code = geom_text_twowaycount_script}

```

```{r}
library(ggplot2)
ggplot(data = mtcars) +
aes(x = cyl, y = gear) +
geom_text_twowaycount()
```

# a geom that is a tile and fills (color) according to count

```{r}
geom_tile_twowaycount_script <- readLines("./R/geom_tile_twowaycount.R")
```

```{r counttile, code = geom_tile_twowaycount_script}

```


```{r}
library(ggplot2)
ggplot(data = mtcars) +
aes(x = cyl, y = gear) +
geom_tile_twowaycount() +
  aes(fill = 1) + 
geom_text_twowaycount(color = "oldlace")
```


# a geom that is a tile and fills (color) according to proportion within column (x)

```{r}
geom_tile_prop_within_x_script <- readLines("./R/geom_tile_prop_within_x.R")
```

```{r proptile, code = geom_tile_prop_within_x_script}

```



```{r}
geom_text_prop_within_x_script <- readLines("./R/geom_text_prop_within_x.R")
```

```{r proptext, code = geom_text_prop_within_x_script}

```


```{r}
library(ggplot2)
ggplot(data = mtcars) +
aes(x = cyl, y = gear) +
geom_tile_prop_within_x(width = .8) +
geom_text_prop_within_x(color = "oldlace") +
  aes(fill = 1)
```
